Dynamics of Laterally Propagating Flames in X-ray Bursts

### 2019-05-14 xrb/paper.tex
some intro refs

@@

%
\author{Chris M.\ Malone}
\affiliation{Los Alamos National Laborary, Los Alamos, NM}

@@

XRB intro

Evidence for localized burning \MarginPar{refs}

>>>>

\author{Donald Willcox}
\affiliation{Lawrence Berkeley National Laboratory, Berkeley, CA}

@@

%

@@

X-ray bursts (XRBs) are thermonuclear explosions of an accreted H or
He layer on the surface of a neutron star (see~\citealt{galloway:2017}
for a review).  Observations of bursts can help constrain the
properties of the underlying neutron star, helping to illuminate the
nuclear equation of state~\citep{steiner:2010,ozel:2010}.  Extensive
observations of XRBs have provided evidence that the burning begins in
a localized region and spreads over the surface of the neutron
star~\citep{bhattacharyya:2006,bhattacharyya:2007}.
